Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-24 draft/ms_v4.tex
PSF color

    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
    and $(i-y)$ PSF colors via comparing the error in color measurements with both
    input magnitudes and input colors.
    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
    estimates for synthetic stars with realistic color distributions down to a very faint
    magnitude.
    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ mag
    is ${\sim}0.025$ mag, and increases to ${\sim}0.11$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag.
    The results are very similar for the $(i-y)$ color.
    We also find that the accuracies of PSF colors do not depend on the input colors of
    the synthetic stars or the seeing conditions.
    For instance, the accuracy of $(g-i)$ color for a bad-seeing \tract{} is only
    slightly worse in the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for a good-seeing \tract{}.

    We further illustrate the accuracies of PSF colors via comparing the distributions
    of colors for the input synthetic stars and the stars recovered by \hscpipe{}
    (see Fig \ref{fig:psf_cdist}).
    Using four different colors and two 2--D color--color planes, we show that the \forced{}
    PSF colors can accurately reproduce the distributions of all four colors and the
    2-D color-color distributions.

    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
    they still have larger uncertainties in colors compared to the relatively isolated
    ones.
    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
    highly blended stars at a fixed input magnitude.
    However, the biases in color measurements for these stars are less severe than
    the magnitude measurements.
    Although the blended stars still show slightly bluer color for $(g-i)$ and slightly redder color for $(i-y)$
    compared to the isolated stars and the input values, the differences in the
    distributions of color uncertainties of blended and isolated stars are less striking
    than the distribution differences for magnitude.

>>>>

    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
    and $(i-y)$ PSF colors via comparing the error in color measurements with both
    input magnitudes and input colors.
    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
    estimates for synthetic stars with realistic color distributions down to very 
    faint magnitude.
    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ 
    mag is ${\sim}0.025$ mag, and it increases to ${\sim}0.11$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag.
    The $(i-y)$ color shows very similar results.
    We also find that the accuracies of PSF colors do not depend on the input colors 
    of the synthetic stars or the seeing conditions.
    For instance, the accuracy of $(g-i)$ color for the bad-seeing \tract{} is only
    slightly worse in the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for the 
    good-seeing \tract{}.

    We further illustrate the accuracies of PSF colors via comparing the distributions
    of colors for the input synthetic stars and the stars recovered by \hscpipe{}
    (see Fig \ref{fig:psf_cdist}).
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors can accurately reproduce the distributions of all four colors 
    and the color-color distributions.

    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
    they still have larger uncertainties in colors compared to the relatively isolated
    ones.
    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
    highly blended stars at a fixed input magnitude.
    Also, for blended stars, the $(g-i)$ color biases toward bluer end while the 
    $(i-y)$ color biases toward redder end.
    However, the biases in color measurements for highly blended stars are less severe 
    than their magnitude measurements.
%% ------------------------------------------------------------------------------------ %%
